---
title: "dev_history.Rmd for working package"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```


# Rmd frist et fusen 

Développer les fonctions nécéssaires à l'appli

L'app doit générer un seul graph avec l'évolution du prenom séléectionné. Néanmoins plusieurs coniguration sont possible pour faire ce graphique, soit via une API, soit via l'interrogation d'une base de données.

### Graph évolution

```{r function}
#' Graphique sur l'evolution d'un prenoms dans le temps
#'
#' @param data deja filter avec le prenom
#'
#' @return
#' ggplot
#' @export
#'
#' @examples
graph_evol <- function(data) {
  ## TODO check names
  
  data %>% 
    ggplot() +
    aes(x = year, y = n) +
    geom_line(color = thinkridentity::thinkr_cols()[1]) +
    labs(x = "Ann\u00E9es", y = "Total naissance", title = paste0("Evolution de ", prenoms))
    theme_bw()
}
```

```{r examples}
data <- prenoms::prenoms %>%
  filter(name == "Vincent" )

graph_evol(data)
```

```{r tests}
test_that("Testing graph", {
data <- prenoms::prenoms %>%
  filter(name == "Vincent" )

graph <- graph_evol(data)

expect_true(inherits(graph, "ggplot"))
})
```


# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
